### 2020-06-05 writeup/experiments.tex
update exp
sec 4

\begin{table}[!b]
\begin{minipage}[t]{.40\textwidth}
	\vspace{-0.1in}
	\centering
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		Sentiment\\ analysis\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf MTL} & {\bf IncTrain} \\
		\midrule
		{\bf MLP}  & 100\% & \textbf{xx\%} \\
		{\bf LSTM} & \textbf{36\%} & xx\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
	\label{tab:taskonomy}
\end{minipage}%
\quad
\begin{minipage}[t]{.58\textwidth}
	\vspace{-0.1in}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
	\label{tab:mtl_better_than_stl}
\end{minipage}
\end{table}

@@

We measure the data efficiency ratio on the sentiment analysis tasks.
In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ ({\cor or $36\%$?}) of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

>>>>

\begin{table}[!b]
\begin{minipage}[t]{.40\textwidth}
	\vspace{-0.1in}
	\centering
	\begin{tabular}{c c c}
		\toprule
		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
		% Sentiment\\ analysis\end{center}\end{minipage}} \\
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{Sentiment analysis} \\
		% \cmidrule(lr){2-3}
		& {\bf all tasks} & {\bf w/o TREC} \\
		\midrule
		{\bf MLP}  & 66\% & 67\% \\
		{\bf LSTM} & 71\% & 71\% \\
		{\bf CNN}  & 63\% & 64\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Efficiency of incremental training compared to baseline MTL.}
	\label{tab:taskonomy}
\end{minipage}%
\quad
\begin{minipage}[t]{.58\textwidth}
	\vspace{-0.1in}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
	\label{tab:mtl_better_than_stl}
\end{minipage}
\end{table}

@@

Our next result shows the incremental training schedule applies to multiple tasks as well.
In Table \ref{tab:taskonomy}, we find that over all six sentiment analysis tasks, incremental training requires less than $71\%$ of the computational cost compared to baseline multi-task training, while achieving the same accuracy averaged over all six tasks.
As a further validation, we exclude TREC from the six tasks and observe similar comparative results.
%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
